Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex
minor curves acknowledgment edit

\section{Acknowledgments}
We are grateful to David Zureick-Brown for introducing us to the
study of stacky canonical rings, for providing invaluable guidance,
and for his mentorship. We also thank Ken Ono and the Emory
University Number Theory REU for arranging our project and
providing a great environment for mathematical learning and
collaboration. We thank Brian Conrad, John Voight, and Shou-Wu
Zhang for helpful comments on this paper. We also thank Jorge Neves
for pointing out the bounds given by Miles Reid's work on the
maximal degrees of minimal generators and relations of spin
canonical rings in high genera. The first author would also like to
mention Joseph Harris and Evan O'Dorney for several enlightening
conversations related to Petri's Theorem. Finally, we gratefully
acknowledge the support of the National Science Foundation (grant
number DMS-1250467). We deeply appreciate all of the support that
has made our work possible.

>>>>

\section{Acknowledgments}
We are grateful to David Zureick-Brown for introducing us to the
study of stacky canonical rings, for providing invaluable guidance,
and for his mentorship. We also thank Ken Ono and the Emory
University Number Theory REU for arranging our project and
providing a great environment for mathematical learning and
collaboration. We thank Brian Conrad, John Voight, and Shou-Wu
Zhang for helpful comments on this paper and thank Jorge Neves
for pointing out the bounds given by Miles Reid's work on the
maximal degrees of minimal generators and relations of spin
canonical rings in high genera. The first author would also like to
mention Joseph Harris and Evan O'Dorney for several enlightening
conversations related to Petri's Theorem. Finally, we gratefully
acknowledge the support of the National Science Foundation (grant
number DMS-1250467). We deeply appreciate all of the support that
has made our work possible.
